Learning Features and Abstract Actions for Computing Generalized Plans

### 2018-11-13 doc/camera-ready/paper.tex
Edit of last paragraph

Finally, problems involving non-deterministic transitions may be
accounted for with a simple change to the SAT theory.
It would be sufficient to replace the formula \eqref{eq:bridge1}
that links $D1$ and $D2$ with a formula that establish that when
$s$ and $t$ are indistinguishable (i.e.\ $\neg D1(s,t)$), then
for each action $a$ on $s$, there is an action $b$ on $t$ whose
set of transitions from $t$ are indistinguishable from the set
of transitions of $a$ on $s$.
To do this, transitions $(s,s')$ in the sample would need to be
tagged with action labels as $(s,a,s')$.

>>>>

Finally, problems involving non-deterministic transitions may be
accounted for with a simple change to the SAT theory.
It would be sufficient to replace the formula \eqref{eq:bridge1}
that links $D1$ and $D2$ with a formula that establishes that when
$s$ and $t$ are indistinguishable (i.e.\ $\neg D1(s,t)$), then
for each action $a$ for $s$, there is an action $b$ for $t$ whose
set of transitions on $t$ is indistinguishable from the set
of transitions of $a$ on $s$; namely, for each transition $(s,a,s')$
there is a transition $(t,b,t')$ with $\Delta_f(s,s')=\Delta_f(t,t')$
for each feature $f$, and vice versa.
To do this, transitions $(s,s')$ in the sample would need to be
tagged with action labels as $(s,a,s')$.
